Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-06 paper.tex
terminando de revisar resultados dos setores de erdos

\subsection{Stable fractions of participants in each Erd\"os sector}\label{subsec:pih}

@@

Typically, $\approx [3-12]\%$ of the vertices are hubs, $\approx [15-45]\%$ are intermediary and $\approx [44-81]\%$ are peripheral, which is consistent with the literature~\cite{secFree}.
These results hold for the total, in and out degrees and strengths.
Stable distributions can also be obtained for 100 or less messages if classification of the three sectors is performed with one of the compound criteria established in Section~\ref{sectioning}. 
The networks hold their basic structure with as few as 10-50 messages,
i.e. concentration of activity and the abundance of low-activity participants take place even with very few messages,
which is highlighted in Section~\ref{si:frac} of the Supporting Information document.
A minimum window size for the observation of more general properties might be inferred by monitoring 
both the giant component and the degeneration of the Erd\"os sectors.

In order to support hypotheses about the generality of these findings,
we obtained the Erd\"os sectors of 12 networks from Facebook, Twitter and Participabr.
The results are given in Table~\ref{tab:secE} of the Supporting Information,
which indicate that the percentages of hubs, intermediary and periphery nodes are essentially the same as for the email lists.

@@

Evident in Table~\ref{tab:pcain},
dispersion is greater in symmetry-related
metrics than in clustering coefficient.
As expected by basic complex network theory, 
peripheral vertices have low values
of centrality metrics
and greater dispersion with respect to clustering coefficient.
%The scatter plot in the third system of Figure~\ref{fig:sym},
%where all metrics are considered and there is a greater dispersion
%with respect to the ordinates,
This reflects in the relevance of the symmetry-related metrics.
We conclude that the symmetry metrics are more powerful,
with respect to dispersion in the topological space,
in characterizing interaction networks
and their participants, than the clustering coefficient,
especially for hubs and intermediary vertices.

>>>>

\subsection{Stable sizes of Erd\"os sectors}\label{subsec:pih}

@@

Typically, $\approx [3-12]\%$ of the vertices are hubs, $\approx [15-45]\%$ are intermediary and $\approx [44-81]\%$ are peripheral, which is consistent with the literature~\cite{secFree}.
These results hold for the total, in and out degrees and strengths.
Stable sizes are also observed for 100 or less messages if classification of the three sectors is performed with one of the compound criteria established in Section~\ref{sectioning}. 
The networks often hold their basic structure with as few as 10-50 messages,
i.e. concentration of activity and the abundance of low-activity participants take place even with very few messages,
which is highlighted in Section~\ref{si:frac} of the Supporting Information document.
A minimum window size for the observation of more general properties might be inferred by monitoring 
both the giant component and the degeneration of the Erd\"os sectors.

In order to support hypotheses about the generality of these findings,
we expose the Erd\"os sector sizes of 12 networks from Facebook, Twitter and Participabr
in Table~\ref{tab:secE} of the Supporting Information document.
The fractions of hubs, intermediary and periphery nodes are essentially the same as for the email lists.

@@

Evident in Table~\ref{tab:pcain} and Figure~\ref{fig:sym},
dispersion is greater in symmetry-related
metrics than in clustering coefficient.
As expected by basic complex network theory, 
peripheral vertices have low values
of centrality measures
and greater dispersion with respect to clustering coefficient.
%The scatter plot in the third system of Figure~\ref{fig:sym},
%where all metrics are considered and there is a greater dispersion
%with respect to the ordinates,
This reflects in the relevance of the symmetry-related metrics.
We conclude that the symmetry metrics are more powerful,
with respect to dispersion in the topological space,
in characterizing interaction networks
and their participants, than the clustering coefficient,
especially for hubs and intermediary vertices.
